A large-scale analysis of racial disparities in police stops across the United

### 2019-12-10 lib/paper_results.Rmd
paper results with p-values before mj changes

City and State outcomes:
```{r disparity-hit_rates-tables}
rbind(
  disp$city$outcome$results$aggregate_hit_rates %>% 
    mutate(
      geography = "cities",
      std_error = sqrt(hit_rate * (1 - hit_rate) / n_search_conducted),
      lower_CI = hit_rate - 1.96 * std_error,
      upper_CI = hit_rate + 1.96 * std_error
    ),
  disp$state$outcome$results$aggregate_hit_rates %>% 
    mutate(
      geography = "states",
      std_error = sqrt(hit_rate * (1 - hit_rate) / n_search_conducted),
      lower_CI = hit_rate - 1.96 * std_error,
      upper_CI = hit_rate + 1.96 * std_error
    )
) %>% 
  select(-std_error) %>% 
  select(geography, everything()) %>%
  kable()
```

>>>>

City and State outcomes:
```{r disparity-hit_rates-tables}
tbl <- rbind(
  disp$city$outcome$results$aggregate_hit_rates %>% 
    mutate(
      geography = "cities",
      std_error = sqrt(average_hit_rate * (1 - average_hit_rate) / average_n_search_conducted),
      lower_CI = average_hit_rate - 1.96 * std_error,
      upper_CI = average_hit_rate + 1.96 * std_error,
    ),
  disp$state$outcome$results$aggregate_average_hit_rates %>% 
    mutate(
      geography = "states",
      std_error = sqrt(average_hit_rate * (1 - average_hit_rate) / average_n_search_conducted),
      lower_CI = average_hit_rate - 1.96 * std_error,
      upper_CI = average_hit_rate + 1.96 * std_error
    )
  ) %>% 
  select(geography, everything())
tbl %>% kable()
ptbl <- tbl %>%
  mutate(
    n_success = average_n_contraband_found,
    n_failure = average_n_search_conducted - average_n_contraband_found
  )
pstate <- filter(ptbl, geography == "states")
pcity <- filter(ptbl, geography == "cities")
```
